\addcontentsline{toc}{chapter}{Bibliografía}

\subsubsection*{Referencias bibliográficas consultadas:}

\bibitem{SWB} ``Semantic Web roadmap''. Tim Berners-Lee. 14/10/1998. \url{https://www.w3.org/DesignIssues/Semantic.html}

\bibitem{OLSW} ``Ontology Learning for the Semantic Web. IEEE Intelligent Systems. Volume 16, Issue 2, March/April 2001, Pages 72-79''. Alexander Maedche, Steffen Staab. Marzo/Abril 2001.

\bibitem{ASW} ``Agents and the Semantic Web. IEEE Intelligent Systems. Volume 16, Issue 2, March/April 2001, Pages 30-37''. Marzo/Abril 2001.

\bibitem{SWR} ``Semantic Web: The roles of XML and RDF. IEEE Internet Computing. Volume 4, Issue 5, September 2000, Pages 63-74''. Stefan Decker, Sergey I. Melnik, Frank Van Harmelen, Dieter Fensel, Michel C.A. Klein, Jeen Broekstra, Michael A. Erdmann, Ian Horrocks. Marzo 2003.

\bibitem{OMSA} ``Ontology mapping: The state of the art. Knowledge Engineering Review. Volume 18, Issue 1, March 2003, Pages 1-31''. Yannis Kalfoglou, Marco Schorlemmer. Marzo 2003.

\bibitem{LDDI} ``Linked Data - Design Issues''. Tim Berners-Lee. 18/06/2009. \url{https://www.w3.org/DesignIssues/LinkedData.html}

\bibitem{PSW} ``Programming the Semantic Web''. Toby Segaran, Colin Evans, Jamie Taylor. Julio 2009.

\bibitem{MMCC} ``Metodologías y métodos para la construcción de ontologías. Scientia Et Technica. Nº 50, Abril de 2012. Páginas 133-140''. Abril 2011.

\bibitem{LSQU} ``Learning SPARQL: Querying and Updating with SPARQL 1.1''. Bob DuCharme. Julio 2013.

\bigskip
\subsubsection*{Recursos web consultados}

\bibitem{OWOL} ``OWL Web Ontology Language''. W3C, 10/02/2004. \url{https://www.w3.org/TR/owl-features/}

\bibitem{RDFS} ``SPARQL 1.1 Query Language''. W3C, 21/03/2013. \url{https://www.w3.org/TR/sparql11-query/}

\bibitem{RDFCAS} ``RDF 1.1 Concepts and Abstract Syntax''. W3C, 25/02/2014. \url{https://www.w3.org/TR/2014/REC-rdf11-concepts-20140225/}

\bibitem{RDFS} ``RDF Schema 1.1''. W3C, 25/02/2014. \url{https://www.w3.org/TR/2014/REC-rdf-schema-20140225/}